<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo = FALSE, eval=TRUE}
knitr::opts_knit$set(
  upload.fun = function(file) knitr::imgur_upload(file, "ce3138fd1186b7d"),
  base.url = NULL) # upload all images to imgur.com
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#"
)
runchunks = TRUE
saveout   = runchunks

if (!runchunks) load('.README.RData')
```
SpiecEasi
=========
[![Build Status](https://travis-ci.org/zdk123/SpiecEasi.svg?branch=pulsar)](https://travis-ci.org/zdk123/SpiecEasi)

## TOC ##
0. [Installation](#installation)
1. [News](#news)
2. [Basic Usage](#basic-usage)
3. [American Gut Data](#analysis-of-american-gut-data)
4. [Using phyloseq](#working-with-phyloseq)
5. [Cross Domain SPIEC-EASI](#cross-domain-interactions)
6. [pulsar & batch options](#pulsar-parallel-utilities-for-model-selection)
8. [Latent Variable Graphical Model](#latent-variable-graphical-model)
9. [Troubleshooting](#troubleshooting)

```{r, child=file.path(system.file(package="SpiecEasi"), "CONTENTS.Rmd")}
runchunks = TRUE
```
